---
title: "OA_Regression"
author: "Yi-Hsuan Tsai"
date: "2/7/2020"
output: html_document
---



```{r}
library(ggplot2)
library(dplyr)
library(readxl)

df <- read_excel("Adops & Data Scientist Sample Data.xlsx",2,col_names = F)
colnames(df) <- c("A","B","C")
```


First, I would like to implement the simple linear regression model.

```{r}
lm1 <- lm(C~A+B, data=df)
par(mfrow=c(2,2))
plot(lm1)
```

We can see that there is an outlier in the model so I would drop it and refit the linear model.
```{r}
df <- filter(df, row_number() != 201)
lm2 <- lm(C~A+B, data=df)
par(mfrow=c(2,2))
plot(lm2)
summary(lm2)
```

The R-squared is not good in this model. It might be a good idea to look at the pair plot of the data to get some insight.

```{r}
pairs(df)
```

We can see that C is pretty different when A or B is below or above zero. And there should be sort of interaction between A and B.
```{r}
# Dummy variable
df$B_positive <- ifelse(df$B>=0, yes=1,no=0 )
df$A_positive <- ifelse(df$A>=0, yes=1,no=0 )

lm3 <- lm(C ~ A*B, df)
summary(lm3)
```

We can see that lm3 is much better than the lm2 with R-squared = 0.7226. Let's do some experiment with the positive term.

```{r}
lm4 <- lm(C ~ A*B*A_positive, df)
summary(lm4)
lm5 <- lm(C ~ A*B*B_positive, df)
summary(lm5)
```

We can see that the lm4 perform super well. Which might imply how this data was generated based on A is positive or negatvie.
So I will choose lm4 as my model.


